Methods and Results

### 2022-10-05 ms.Rmd
Fixed lnSD and Al double checked. As I figured, we need to reverse ref level. Slightly confusing, but makes sense

```
# Methods
#### Standardised Effect Size Measure
We used the standardised mean difference with a small sample correction (i.e., Hedges' *g*) as our measure of effect size comparing female fitness measures across experimental treatments. To correct for the possibility that population variances in the two treatments differ, we made use of a corrected version of Hedges' *g* that controls for heteroscedastic population variances (hereafter called SMDH; [@Bonnet2008; @Bonnett2009]). Effect sizes were calculated by subtracting the control group mean from the treatment group mean and dividing by the pooled standard deviation. As such, positive effect sizes indicate that female 'fitness/traits' in control groups was higher than female 'fitness/traits' in treatment groups.

@@

    # First, we need to reorganise the data in long format

    data_long <- data %>% pivot_longer(cols = c(14:19), values_to = "value") %>% 
                pivot_wider(names_from = grep(name, "sd"), values_from = value, ) %>% data.frame()

    data_long_mean <- data_long %>% filter(grepl("X_", name)) %>% mutate(obs = 1:n())
      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)
       data_long_n <- data_long %>% filter(grepl("N_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)

    # Now, merge data sets together.

       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
        final_long <- left_join(final_long1, data_long_n, by = "obs")

@@

>>>>

```
# Methods
#### Standardised Effect Size Measures
We used the standardised mean difference with a small sample correction (i.e., Hedges' *g*) as our measure of effect size comparing female fitness measures across experimental treatments. To correct for the possibility that population variances in the two treatments differ, we made use of a corrected version of Hedges' *g* that controls for heteroscedastic population variances (hereafter called SMDH; [@Bonnet2008; @Bonnett2009]). Effect sizes were calculated by subtracting the treatment group mean from the control group mean and dividing by the pooled standard deviation. As such, positive effect sizes indicate that female 'fitness/traits' in control groups was higher than female 'fitness/traits' in treatment groups.

We also tested whether the variability in female fitness between the control and treatment group differed. To test this question, we used two effect size measures, the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups (contrast-based effect size), and the log standard deviation (lnSD), controlling for the log mean (lnX) using an arm-based approach [@nakagawa2015meta]. Both methods assume a mean-variance relationship, which was clearly evident in our data (see Supp Fig. SX). However, lnCVR assumes a linear relationship on the natural scale (SD-Mean), whereas lnSD fit using an arm-based approach assumes they are linear on the log scale, but relaxes assumptions about how the mean and variance scale.

@@

    # First, we need to reorganise the data in long format
    data_long <- data %>% filter(geary_test == "pass") %>%  
                pivot_longer(cols = c(14:19), values_to = "value", names_to = "name") %>% 
                data.frame()

    data_long_mean <- data_long %>% filter(grepl("X_", name))  %>% 
                      mutate(obs2 = 1:n())
      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% 
                      mutate(obs2 = 1:n()) %>% 
                      select(obs2, name, value)
       data_long_n <- data_long %>% filter(grepl("N_", name))  %>% 
                      mutate(obs2 = 1:n()) %>% 
                      select(obs2, name, value)

    # Now, merge data sets together. Note that, we want to do some renaming and we need to remember that lnCVR is subtracting the CONTROL - TREATMENT, but we need to flip this around in lnSD model because it's TREATMENT - CONTROL.

       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs2")
        final_long <- left_join(final_long1, data_long_n, by = "obs2") %>% 
                      rename("sd" = value.y,
                             "mean" = value.x,
                             "n"  = value,
                             "trt" = name.x) %>% 
                      mutate(trt = relevel(as.factor(trt), ref = "X_T"),
                             study.obs = paste0(obs, "_", study))

    # Now that we have it in long format, we can calculate lnSD and lnX and associated SE's for lnSD which can be accounted for in meta-analysis

        final_long <- escalc(sdi = sd, ni = n,  
                             measure = "SDLN", data = final_long, 
                             append = TRUE, var.names=c("lnSD","v_lnSD"))

         final_long <- escalc(mi = mean, sdi = sd, ni = n,  
                              measure = "MNLN", data = final_long, 
                              append = TRUE, var.names=c("lnX","v_lnX"))
        # write long_data for checking
         write.csv(final_long, file = "./data/meta_dat_long.csv", row.names = FALSE)

    # Fit a MLMA model with metafor
        model1_lnSD <- rma.mv(lnSD ~ 1 + trt + lnX, V = v_lnSD, 
                       random = list(~1 + trt|study.obs, 
                                     ~1 | study,
                                     ~1|obs2, 
                                     ~1|species), 
                       dfs = "contain", test = "t", 
                       method = "REML", data = final_long)
robust_model1_lnSD <- robust(model1_lnSD, cluster = final_long$study, vcov = "CR2")

@@

  data_cvr %>% ggplot(aes(y = 1/ sqrt(v_logCVR), x = mean(logCVR))) + geom_point()
